\chapter{Testing}

\subsection{Unit Testing}
\begin{itemize}
    \item \textbf{Cell Management Module}: Verify the correct addition, deletion, and reallocation of cells and prisoner placements within the database.
    \item \textbf{Staff Management Module}: Ensure accurate registration, removal of staff, and management of user access rights.
    \item \textbf{Job Management Module}: Test the functionality of adding, updating, and deleting prisoner job assignments.
    \item \textbf{Crime Management Module}: Validate the addition, modification, and removal of crime details associated with prisoners.
    \item \textbf{Prisoner Management Module}: Confirm accurate addition, updating, and deletion of prisoner records in the system.
    \item \textbf{Visitor Management Module}: Verify registration and deletion of visitor records, ensuring they link accurately to prisoners.
    \item \textbf{Work Management Module}: Ensure correct recording of work details, removal of work records, and calculation of total work hours for prisoners.
\end{itemize}

\subsection{Integration Testing}
\begin{itemize}
    \item \textbf{Prison Management System Integration}: Assess the collective performance of Cell, Staff, Job, Crime, Prisoner, Visitor, and Work Management modules to ensure they work together seamlessly.
\end{itemize}

\subsection{System Testing}
\begin{itemize}
    \item \textbf{End-to-End Functionality}: Test end-to-end functionality to ensure the system meets all requirements for prisoner management, cell allocation, staff operations, and work logging.
\end{itemize}

\subsection{User Acceptance Testing (UAT)}
\begin{itemize}
    \item \textbf{Administrative Tasks}: Evaluate the usability of the system by having administrators perform tasks like adding prisoners, reallocating cells, and managing job details.
\end{itemize}

\subsection{Security Testing}
\begin{itemize}
    \item \textbf{User Authentication Measures}: Examine the authentication system for vulnerabilities, ensuring only authorized access.
    \item \textbf{Data Encryption}: Validate the encryption of sensitive prisoner and staff data within the system.
    \item \textbf{Access Control}: Confirm the access control mechanisms to prevent unauthorized actions and data breaches.
\end{itemize}

\subsection{Performance Testing}
\begin{itemize}
    \item \textbf{Concurrent User Actions}: Assess system performance when handling multiple concurrent tasks, such as adding prisoners, reallocating cells, or updating job details.
\end{itemize}

\subsection{Regression Testing}
\begin{itemize}
    \item \textbf{Impact of Changes}: Ensure modifications to the Cell, Staff, or other modules do not affect existing functionalities in unintended ways.
\end{itemize}

\subsection{User Interface (UI) Testing}
\begin{itemize}
    \item \textbf{Consistency and Responsiveness}: Review UI elements for visual consistency and responsiveness across different screens and user roles.
\end{itemize}

\subsection{Error Handling Testing}
\begin{itemize}
    \item \textbf{Error-Triggering Scenarios}: Subject the system to various error-prone scenarios (e.g., invalid data inputs or network failures) to ensure proper error messages and handling.
\end{itemize}

\subsection{Load Testing}
\begin{itemize}
    \item \textbf{System Capacity}: Test the system's ability to handle a high volume of prisoner records, visitor registrations, and staff actions simultaneously.
\end{itemize}

\subsection{Compatibility Testing}
\begin{itemize}
    \item \textbf{Cross-Browser and Cross-Device Compatibility}: Ensure that the system functions correctly across different browsers and devices used by staff.
\end{itemize}

\subsection{Usability Testing}
\begin{itemize}
    \item \textbf{User Experience Evaluation}: Collect feedback on the ease of use, intuitiveness, and efficiency of the system to identify areas for improvement.
\end{itemize}
